### 2018-09-19 Paper_HTML/Paper_HTML.Rmd
update Painel 2

<img class=img1 src="Logo2.png" style="float: left; width: 30%;height: auto;" hspace="20px;">
<div class="title2">
  <p class="title">Laboratório de Aprendizado de Máquina em Finanças e Organizações</p>
  <p class="alignright"> <a href="http://lamfo.unb.br/">http://lamfo.unb.br </a> </p>
</div>

@@

opts_knit$set(root.dir = "C:/Users/rafal/Google Drive/LAMFO/AutomationJobs")

@@

The study about automation and digitalization and how these scenarios can affect the jobs around the world is continuously updated year by year. This statement is in line with what was said by @raj2018ai. @raj2018ai asserts that the current body of empirical literature surrounding robotics and Machine Learning adoption by organizations is growing and often trying to answer similar questions: Will be the automation the end of the traditional work ? Some discrepancies, however, have been found in several papers and these discrepancies highlight the need for further inquiry, replication studies and more complete and detailed data.

Furthermore, these new technological advancements have led to both excitements about the capability of Machine Learning algorithms and automation to boost economic growth and also the concern about the fate of human workers in a world in which computer algorithms can perform many of the functions that a human can [@furman2016time]. In this sense, [@raj2018ai] reported that recent academic research, suggests that automation and robotics may have been responsible for about one-tenth of the increase in the US's gross domestic product (GDP) between 1993 and 2007 [@graetz2017modern] but also a decrease in the number of job positions [@frey2017future].

@ramaswamy2018technological define automation when a machine does work that might previously have been done by a person, and nowadays, most of the routine manual, nonroutine manual and some routine cognitive and nonroutine cognitive types of jobs cab me automatized. @autor2003skill presented how the fast adoption of computer technologies change the tasks performed by workers at their jobs.  Another definition is given by @chui2015four who assessed the "automatability" of those capabilities through the use of current, leading-edge technology, adjusting the level of capability required for occupations where work occurs in unpredictable settings.

The main article about this theme reported by the literature is the job of and @frey2013future and @frey2017future. @frey2017future estimated the susceptibility of employment to computerization. In their paper, the authors classify occupations in the US with respect to the risk of being susceptible to automation by asking experts about the technological potential for automation in the near future and applying a Gaussian Process Classifier for 702 occupations. This was accomplished through the previous classification, 
for some occupations labeled by experts and the extrapolating the probability for all data. As a result, @frey2017future reported that 47% of all persons employed in the US are working in jobs that could be performed by computers within the next 10 to 20 years.

A similar idea as the proposed by @frey2017future was applied for other countries. @pajarinen2014computerization suggest that 35.7 percent of Finnish jobs are at high risk to automation, @diba2015roboter estimate the share of jobs at risk of automation to be as high as 59% in Germany, @bowles2014computerisation finds the share of jobs that are susceptible to automation in Europe to range between 45% to more than 60% and @arntz2016risk estimated the job automatability of jobs for 21 Organization for Economic Co-operation and Development (OECD) countries.

In our perspective the most embracing paper is given by @arntz2016risk. In their paper the authors take into account the heterogeneity of workers' tasks within occupations and found that, on average across the 21 OECD countries, 9% of jobs are automatable. However, the authors found heterogeneity across the OECD countries and highlighted that while the share of automatable jobs is 6% in Korea, the corresponding share is 12% in Austria, this difference according to the authors can be a reflex of general differences in workplace organizations or education of workers across countries. @arntz2016risk indeed did not study Brazil which is an OECD.

@arntz2016risk also found that despite the cross-country differences, the main feature of all OECD countries is that the automatability frequently decreases in the level of education and in the income of the workers. For all types of workers @arntz2016risk suggest that it is mostly low skilled and low-income individuals who face a high risk of being automatable which is concordant with @bakhshi2015creativity findings.

@goos2014explaining and @david2013growth found that in the US and Europe has been the "polarization" of employment by skill level and the, therefore, the inequality in wage incomes between all types of occupations.

@acemoglu2017robots examine the impact of the increase in industrial automation in U.S. labor markets between 1990 and 2007. The authors found that automation in the United States is negatively correlated with employment and wages during 1990 and 2007. @acemoglu2017robots also estimated that each additional robot reduced employment by six workers and that one new robot per thousand workers reduced wages by 0.5 percent. This effect according to the authors is most pronounced in manufacturing, particularly in a routine manual and blue-collar occupations (routine cognitive), and for workers without a college degree.

In the same direction @bessen2018ai affirms that in manufacturing, technology has sharply reduced jobs in recent decades. The author presented a model of demand that predicted the rise and fall of employment in the textile, steel and automotive industries which were the most vulnerable sectors with respect to automatization.

@furman2018should for instance, argues that instead, the concern is that the process of turnover, in which workers displaced by automatization find new employment as technology gives rise to new consumer demands and consequently new jobs, could lead to sustained periods of time with a large fraction of people not working which can be fatal for the countries' economy.

@ramaswamy2018technological summarizes most of the findings of this theme:

@@

@ramaswamy2018technological argues that The risks of job automation in developing countries are found to vary across countries, for example, the author says that it is estimated to range from 55% in Uzbekistan to 85% in Ethiopia. In emerging economies, the risk of automation is estimated to be relatively high with 77% of jobs in China and 69% in India found to be at risk.

While most of the studies used the occupations description and some expert opinion, @mann2017benign took a different approach to analyze the effects of automation on employment. In their study, the authors rely on information provided from granted patents. @mann2017benign applied a apply a machine learning classifier algorithm to all 5 million U.S. patents granted between 1976 and 2014 to identify patents related to automation based on a sample of 560 manually classified patents to sort patents into automation and non-automation innovations. @mann2017benign concluded that though automation causes manufacturing employment to fall, it increases employment in the service sector, and overall has a positive impact on employment. In the same direction @susskind2017model argue that the range of tasks which robots can substitute could be much larger.

Another work that presents an optimistic overview of the theme is the @bessen2017automation's paper. The author found that new technologies should have a positive effect on employment if they improve productivity in markets where there is a large amount of unmet demand. He also suggests that new computer technology is associated with employment declines in manufacturing, where demand has generally been met but is correlated with employment growth in less saturated, non-manufacturing industries.

According to @furman2018should since automatability can reduce the number of job positions for the less-skilled jobs this can imply in a decline the demand for higher-skilled jobs as well. In the other hand, higher-skill jobs that use problem-solving capabilities, creativity, and intuition (nonroutine cognitive tasks), likewise as lower-skill jobs that require situational adaptability and in-person interactions (routine cognitive), were less likely to be automatized.

With respect to the literature review, we can observe that both optimistic and pessimistic scenarios are possible. If we assume that machines can only be a substitute for routine jobs @acemoglu2011skills then the result is likely to be optimistic or less pessimistic. This is explained by @acemoglu2016race which argues that this is due to two reasons: first, because there always will remain, classes of occupations, not totally automatized automation and second, always is possible the introduction of new tasks in which labor has a comparative advantage as pointed by @acemoglu2016race and that can offset the loss of occupations due to automation.

None of the cited papers studied Brazil and the impact of an economic crisis in the number of job positions classified by the level of complexity or probability of automatization. Hence, we proposed to estimate the probability of automation of the Brazil's Occupational classification System (<i>Classificação Brasileira de Ocupações</i> - CBO) associating this probability with the O\*NET job zones classification and also measuring the effect of the 2015-2018 Brazilian economic crisis in the number of job positions for the five job zoned defined by O*NET classification system.

@@

kable(tab1, caption = "Percent of change between levels to level 1 over the years.", format.args = list(decimal.mark = ","),booktabs=TRUE)
```

@@

kable(tab2, caption = "Fall percentage from  2014 to 2016 in the CGR.")
```

@@

kable(tab3, caption = "Fields and researchers' answers in the survey.")
```

@@

>>>>

<img src="Logo2.png" style="float: left; width: 30%;height: auto;" hspace="20px;">
<div class="title2">
  <p class="title">Laboratório de Aprendizado de Máquina em Finanças e Organizações</p>
  <p class="alignright"> <a href="http://lamfo.unb.br/">http://lamfo.unb.br </a> </p>
</div>

@@

# opts_knit$set(root.dir = "C:/Users/rafal/Google Drive/LAMFO/AutomationJobs")
opts_knit$set(root.dir = "C:/Users/B2657804/Google Drive/LAMFO/AutomationJobs")

@@

O estudo sobre automação e digitalização e como esses cenários podem afetar os empregos em todo o mundo é continuamente atualizado ano a ano. Esta declaração está de acordo com o que foi dito por @raj2018ai. @raj2018ai afirma que o atual corpo de literatura empírica em torno da robótica e adoção de Machine Learning pelas organizações está crescendo e muitas vezes tentando responder a perguntas semelhantes: Será que a automação será o fim do trabalho tradicional? Algumas discrepâncias, no entanto, foram encontradas em vários estudos e essas discrepâncias evidenciam a necessidade de novas investigações, artigos de replicação e dados mais completos e detalhados.

Além disso, esses novos avanços tecnológicos levaram tanto à motivação sobre a capacidade dos algoritmos de Aprendizado de Máquina quanto à automação para impulsionar o crescimento econômico e também a preocupação com o destino dos trabalhadores humanos em um mundo no qual os algoritmos de computador podem executar muitas das funções humanas [@furman2016time]. Nesse sentido, @raj2018ai relatou que pesquisas acadêmicas recentes sugerem que automação e robótica podem ter sido responsáveis por cerca de um décimo do aumento do Produto Interno Bruto (PIB) dos EUA entre 1993 e 2007 [@graetz2017modern] mas também uma diminuição no número de postos de trabalho [@frey2017future].

@ramaswamy2018technological define automação quando uma máquina faz trabalho que poderia ter sido realizado anteriormente por uma pessoa, e hoje em dia, a maioria das tarefas manuais rotineiras, manuais não rotineiros e alguns tipos de tarefas rotineiras cognitivas e não rotineiras podem ser automatizados. @autor2003skill apresentou como a adoção rápida de tecnologias de computação altera as tarefas executadas pelos trabalhadores em seus trabalhos. Outra definição é dada por @chui2015four que avaliou o "automatismo" dessas capacidades através do uso de tecnologia atual de ponta, ajustando o nível de capacidade requerido para ocupações onde o trabalho ocorre em configurações imprevisíveis.

Os principais artigos sobre este tema relatados pela literatura científica são os trabalhos de @frey2013future e @frey2017future. @frey2017future estimou a suscetibilidade do emprego à informatização. Em seu artigo, os autores classificam as ocupações nos EUA com relação ao risco de serem suscetíveis à automação, perguntando aos especialistas sobre o potencial tecnológico de automação em um futuro próximo e aplicando um Classificador de Processo Gaussiano para 702 ocupações. Isso foi realizado através da classificação a priori, de algumas ocupações rotuladas por especialistas e a extrapolação da probabilidade para todos os dados. Como resultado, @frey2017future relatou que 47% de todas as pessoas empregadas nos EUA estão trabalhando em trabalhos que poderiam ser executados por computadores nos próximos 10 a 20 anos.

Uma ideia semelhante à proposta por @frey2017future foi aplicada a outros países. @pajarinen2014computerization sugere que 35,7% dos empregos na Finlândia estão sob alto risco para automação, @diba2015roboter estima que a parcela de empregos sob risco de automação chegue a 59% na Alemanha, @bowles2014computerisation encontra que a parcela de postos de trabalho que são suscetíveis à automação na Europa varia entre 45% à mais de 60% e @arntz2016risk estimou a automatização do trabalho dos 21 países da Organização para Cooperação e Desenvolvimento Econômico (OCDE).

Em nossa perspectiva, o mais abrangente o trabalho sobre o tema é devido a @arntz2016risk. Em seu artigo, os autores levam em conta a heterogeneidade das tarefas dos trabalhadores nas ocupações e descobriram que, em média, nos 21 países da OCDE, 9% dos empregos são automatizáveis. No entanto, os autores encontraram heterogeneidade entre os países da OCDE e destacaram que, enquanto a parcela de empregos automatizáveis é 6% na Coréia, a participação correspondente é de 12% na Áustria, essa diferença de acordo com os autores pode ser um reflexo das diferenças gerais das organizações de trabalho, ou devido ao nível educacional desses trabalhadores em todos os países. @arntz2016risk de fato não estudou o Brasil, o qual não é mebro da OCDE. Dessa forma, há a possibilidade de atender a uma lacuna nesse campo de estudo usando dados nacionais.

@arntz2016risk também constatou que, apesar das diferenças, a principal característica de todos os países da OCDE é que a capacidade de automação frequentemente diminui com o nível de educação bem como a renda dos trabalhadores. Para todos os tipos de empregados, @arntz2016risk sugerem que os indivíduos de baixa qualificação e renda são os que enfrentam um maior risco de terem seus postos de trabalho automatizáveis, este resultado é concordante com os achados @bakhshi2015creativity.

@goos2014explaining e @david2013growth descobriram que nos EUA e na Europa tem sido a "polarização" do emprego por nível de habilidade a principal causa da desigualdade na renda salarial entre todos os tipos de ocupações.

@acemoglu2017robots examinam o impacto do aumento da automação industrial nos mercados de trabalho dos EUA entre 1990 e 2007. Os autores descobriram que a automação nos Estados Unidos está negativamente correlacionada com emprego e salários durante 1990 e 2007. @acemoglu2017robots também estimaram que cada máquina adicional reduziu o emprego em seis trabalhadores e que um novo robô por mil trabalhadores reduziu os salários em 0,5%. Este efeito, de acordo com os autores, é mais pronunciado na manufatura, particularmente em ocupações manuais e manuais de rotina (tarefas rotineiras cognitivas) e para trabalhadores sem diploma universitário.

Na mesma direção, @bessen2018ai afirma que no setor de manufatura, a tecnologia reduziu drasticamente os empregos nas últimas décadas. O autor apresentou um modelo de demanda o qual previa a ascensão e queda do emprego nas indústrias têxtil, siderúrgica e automobilística. Estes setores eram os mais vulneráveis no que diz respeito à automatização.

@furman2018should, por exemplo, argumenta que apesar da tecnologia gerar novas demandas de consumo e consequentemente novos empregos, a rotatividade causada pela automação poderia levar a períodos de alto desemprego. Isto pode ser fatal para a economia dos países.

@ramaswamy2018technological resume a maioria das descobertas deste tema:

@@

@ramaswamy2018technological argumenta que o risco de automação de trabalho em países em desenvolvimento varia entre países, por exemplo, o autor afirma que é estimado para variar de 55% no Uzbequistão até 85% na Etiópia. Nas economias emergentes, estima-se que o risco de automação seja relativamente alto, com 77% de empregos na China e 69% na Índia considerados em risco.

Enquanto a maioria dos estudos utilizou a descrição das ocupações e algumas opiniões de especialistas, @mann2017benign adotou uma abordagem diferente para analisar os efeitos da automação no emprego. Em seu estudo, os autores utilizaram em informações fornecidas por patentes concedidas. @mann2017benign aplicou um algoritmo classificador de Aprendizado de Máquina a todas as 5 milhões de patentes concedidas entre 1976 e 2014 para identificar patentes relacionadas à automação com base em uma amostra de 560 patentes classificadas manualmente para classificar patentes em inovações de automação e não-automação. @mann2017benign concluiram que, embora a automação reduza o emprego industrial, aumenta o emprego no setor de serviços e, em geral, tem um impacto positivo no emprego. Na mesma direção, @susskind2017model argumenta que o número de tarefas que os robôs podem substituir pode ser ainda muito maior.

Outro trabalho que apresenta uma visão geral otimista do tema é o artigo de @bessen2017automation. O autor descobriu que as novas tecnologias devem ter um efeito positivo no emprego, se melhorarem a produtividade em mercados onde há uma grande quantidade de demanda reprimida. Ele também sugere que a nova tecnologia de computadores está associada a declínios de emprego na indústria, onde a demanda é geralmente alcançada, mas está correlacionada com o crescimento do emprego em indústrias menos saturadas e não-manufatureiras.

Outro trabalho que apresenta uma visão otimista do tema é o artigo de @bessen2017automation. Segundo o autor, as novas tecnologias devem ter um efeito positivo sobre o emprego se melhorarem a produtividade em mercados onde há uma grande quantidade de demanda reprimida. Também é sugerido que a nova tecnologia está associada ao declínio do emprego na indústria manufaturada, onde a demanda está correlacionada ao crescimento do emprego em indústrias menos saturadas e não manufatureiras.

De acordo com @furman2018should, uma vez que a automatização pode reduzir o número de postos de trabalho para os empregos menos qualificados, isso também pode implicar em um declínio da demanda por empregos mais qualificados. Por outro lado, tarefas mais qualificadas que usam capacidades de resolução de problemas, criatividade e intuição (tarefas cognitivas não-rotineiras), assim como tarefas de baixa qualificação que exigem adaptabilidade situacional e interações pessoais (cognitiva de rotina), são menos propensas a serem automatizados.

Com relação à revisão de literatura, podemos observar que cenários otimistas e pessimistas são possíveis. Se assumirmos que as máquinas só podem ser substitutas de tarefas de rotina [@acemoglu2011skills], então o resultado provavelmente será otimista ou menos pessimista. Isto é explicado por @acemoglu2016race, que argumenta que isto é devido a duas razões: primeiro, porque sempre haverá classes de ocupações que não serão totalmente automatizadas, e segundo, sempre é possível a introdução de novas tarefas em que o trabalho tem uma vantagem comparativa, como apontado por @acemoglu2016race. Isto pode compensar a perda de ocupações devido à automação.

Nenhum dos artigos citados estudou o Brasil e o impacto de uma crise econômica no número de postos de trabalho classificados pelo nível de complexidade ou probabilidade de automatização. Assim, propusemo-nos a estimar a probabilidade de automação da Classificação Brasileira de Ocupações - CBO, associando essa probabilidade com a classificação de zonas de trabalho (*Job Zones*) do O\*NET. Também é medido o efeito da crise econômica brasileira de 2015-2018 no número de postos de trabalho para os cinco *Job Zones* definidos pelo sistema de classificação O\*NET.

@@

kable(tab1, caption = " ", format.args = list(decimal.mark = ","),booktabs=TRUE)
```

<center style="padding-bottom:20px;">Tabela 1: Percent of change between levels to level 1 over the years.</center>

@@

kable(tab2, caption = " ")
```

<center style="padding-bottom:20px;">Tabela 2: Fall percentage from  2014 to 2016 in the CGR.</center>

@@

kable(tab3, caption = " ")
```

<center style="padding-bottom:20px;">Tabela 3: Fields and researchers' answers in the survey.</center>

@@

```{r save}
saveRDS(ggplotly(a), "Box_Paper.RDS")
saveRDS(p, "Serie_Paper.RDS")
```
